\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2018-01-08 HOPS/photometry/ms.tex
updated to latest post submitted

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider systematic differences in the underlying protostar population as a possible cause for the observed correlations in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}.  \cite{ali} show that \herschel\ colors are highly correlated with the assumed envelope properties, especially, the infall rate and the envelope mass. In fact, \cite{ali} find protostellar envelopes to be the dominant factor affecting the observed colors in the \herschel\ bands.  Thus, if the correlations in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} reflect actual population differences in the subregions, then the envelope properties are likely to be the actual underlying cause of said differences.
\par
One explanation for this difference is that the protostars are, simply, at different stages of development in each sub-region.  The observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may then be viewed as differences in the evolutionary epoch of the protostars.  To further explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required, in this scenario, to have transferred more of their mass in the central cores to be consistent with their redder colors.  If we assume that the fundamental star-formation process responsible for the protostellar evolution is the same across the sub-regions, then the systematic differences in the evolutionary epochs of the protostars could have come from differences in the onset of the start-formation itself.  Alternatively, the sub-regions with higher local gas+dust density may speed up protostellar evolution because free-fall collapse time-scales are dependent on the local density of material.  Or, the availability of gas and dust contributing to the envelope is systematically different between the sub-regions.  Finally, the central cores may be systematically more massive in regions with redder colors because of actual differences in the local gas+dust content and/or the accretion process itself.
\par
Unfortunately, we lack the data needed to definitively identify which of the above scenarios (or something else entirely) may be responsible for the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}, if said trend is produced by differences in the population of protostars in each subregion.  Future work combining detailed studies of the local gas+dust content may provide additional constraints.  However, we also cannot rule out that the protostars in the sub-regions were led to different evolutionary states by some fundamental and unknown difference in the star-formation process itself.

\section{Conclusions}
\label{sec:conc}

We explored the mid- to far-infrared properties of the Orion protostars obtained as part of the \herschel Key Program HOPS. Investigations of the observed properties of these protostars reveal apparent correlations as a function of sub-regions in both the Orion A and B clouds.  We investigated the role of bias introduced due to differences in completeness limits in these correlations by artificially introducing a completeness limit in the LDN~1641 sub-region and comparing the resulting changes in median flux ratio to Orion~OMC-2/3 values. These simulations suggest that completeness limit bias alone is not sufficient to explain the observed correlation for \clrb.  An alternative explanation may be population differences between these sub-regions. We offer
differences in accretion properties and/or evolutionary status as the cause for the population differences. We note that both accretion properties and evolutionary status trace fundamental differences in the star-forming conditions in the environment, notably higher gas+dust content.  This contribution focused entirely on the observed photometry and flux ratios.   Companion publications will explore the environmental differences by examining derived quantities such as bolometric properties and classification.

>>>>

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider systematic differences in the underlying protostar population as a possible cause for the observed correlations in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}.  \cite{will} provide observational evidence for such a scenario.  \cite{will} derived bolometric luminosities and temperatures of our HOPS protostar sample and find statistical differences in the bolometric properties of the protostars as a function of the sub-region in Orion~A~and~B clouds.  The authors argue that these differences track an underlying difference in the star-formation rate across the sub-regions leading to a different mixture of protostars and more evolved objects.  Their findings are supported, in part, by evidence that the fractions for both Class~0 stars and PBRs compared to Class~I~and~II objects are also different in the subregions \citep{pbrpaper}.
\par
Indeed, \cite{ali} show that \herschel\ colors are highly correlated with the assumed envelope properties, especially, the infall rate and the envelope mass. In fact, \cite{ali} find protostellar envelopes to be the dominant factor affecting the observed colors in the \herschel\ bands.  Given that large, active envelopes are the defining characteristics of Class~0 objects and PBRs, the correlations apparent in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are consistent with the population differences suggested by \cite{will}.

\section{Conclusions}
\label{sec:conc}
We explored the mid- to far-infrared properties of the Orion protostars obtained as part of the \herschel Key Program HOPS. Investigations of the observed properties of these protostars reveal apparent correlations as a function of sub-regions in both the Orion A and B clouds.  We investigated the role of bias introduced due to differences in completeness limits in these correlations by artificially introducing a completeness limit in the LDN~1641 sub-region and comparing the resulting changes in median flux ratio to Orion~OMC-2/3 values. These simulations suggest that completeness limit bias alone is not sufficient to explain the observed correlation for \clrb.  An alternative explanation may be population differences between these sub-regions. We offer
differences in accretion properties and/or evolutionary status as the cause for the population differences. We note that both accretion properties and evolutionary status trace fundamental differences in the star-forming conditions in the environment, notably higher gas+dust content.  This contribution focused entirely on the observed photometry and flux ratios.   Companion publications will explore the environmental differences by examining derived quantities such as bolometric properties and classification.
